FoRTE baseline

### 2019-07-04 analysis/paper/paper.Rmd
Write results for uncertainty barplot

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(9, 4)}
within_vs_across_cap <- paste(
  "Comparison of parameteric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```

@@

The importance of structural uncertainty relative to parameter uncertainty depended on the state variable in question.
Uncertainty in gross and net primary productivity...

Take-away: Overall, structural uncertainty (variance in ensemble means across structures) is comparable or lower than parameter uncertainty (uncertainty within ensembles for a given structure).
Parameter uncertainty varies significantly across model structures.
Enabling trait plasticity increases variance in predictions of AGB.
Enabling the finite canopy radius increases the variance in LAI predictions.
GPP and NPP have the highest variance by far for the combination of finite canopy radius and two-stream radiative transfer.

>>>>

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(9, 4)}
within_vs_across_cap <- paste(
  htmlfig(),
  "Comparison of parameteric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```

@@

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question. 
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) led to reduced predictive uncertainty for all four variables considered, with the largest uncertainty reduction for gross and net primary productivity.
Meanwhile, facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) substantially reduced uncertainty in aboveground biomass and slightly reduced uncertainty in gross and net primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index and aboveground biomass, but did not have a consistent effect on uncertainty in predictions of productivity.
